Practical Hilbert space approximate Bayesian Gaussian processes for probabilistic programming

### 2022-03-09 Paper/Manuscript_Stats&Comp/reply_letter_STCO.tex
More edits to R1 responses in reply letter

In response, we have developed and presented a diagnostic procedure that consists of iterative steps to fit and diagnose the model. Numerical equations are used to set initial values and update the key parameters in each iterative step. The recommended diagnostic procedure allows to automatize the application of the method. In the revised manuscript, please see Section 4.5 and examples in Section 4.6, Case studies, and Appendix C, for more details.

@@

Section 4 has been re-structured and updated by adding new subsections. In particular this includes, a subsection on the theoretical evidence of near linear proportionality among the key hyperparameters of the model, a subsection with the experimentation and resulting numerical diagnostic equations, a subsection supporting, detailing, and discussing on the diagnostic rules, and a subsection analyzing the performance of the diagnostic tool. Additionally, new subsections regarding how to proceed with other different kernels from those implemented in this study and some insights on how the method performs in multi-dimensional cases have been added.

We have simplified and significantly improved the writing in Section 5. We have also focused the case studies more on the main goals of the paper, which are: 1) to facilitate the implementation of the method for practical users providing clear a formulation of the method, and 2) and to provide an easy and general diagnostic tool to achieve good approximations via HSGPs.

>>>>

We completely agree and consequently, we have developed and described an automatic iterative diagnostic procedure for fitting and diagnosing the model. Numerical equations are used to set initial values and update the key parameters in each iterative step.
% The recommended diagnostic procedure allows to automatize the application of the method. 
In the revised manuscript, please see Section 4.5 and examples in Section 4.6, Case studies, and Appendix C, for more details.

@@

Section 4 has been re-structured and updated by adding new subsections:
\begin{itemize}
	\item a subsection on the theoretical evidence of near linear proportionality among the key hyperparameters of the model
	\item a subsection with the experimentation and resulting numerical diagnostic equations
	\item a subsection supporting, detailing, and discussing on the diagnostic rules
	\item a subsection analyzing the performance of the diagnostic tool
\end{itemize}

%Additionally, new subsections regarding how to use other kernels from those implemented in this study and some insights on how the method performs in multi-dimensional cases have been added.

We have simplified and significantly improved the writing in Section 5. We have also adapted the case studies to be more aligned with the main goals of the paper, which are: 1) to facilitate the implementation of the method for practical users providing clear a formulation of the method, and 2) and to provide an easy and general diagnostic tool to achieve good approximations via HSGPs.
